XXXXX

### 2014-09-29 paper/paper1.tex
validated R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS

A matching triple has any predicate except those excluded by the '-' operator.

\begin{ex}
<FeelingForce> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute xsd:string }
<JediMentor> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute 'good'^^xsd:string ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
    :mentorOf @<JediStudent> ,
    - :studentOf @<JediMentor> }
<JediStudent> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute 'good'^^xsd:string ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
    - :mentorOf @<JediStudent> ,
    :studentOf @<JediMentor> }
\end{ex}

@@

\begin{ex}
:Obi-Wan 
    :feelingForce 'true'^^xsd:boolean ;
    :attitute 'good'^^xsd:string ;
    :laserSwordColor 'blue'^^xsd:string ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
    :mentorOf :Anakin .
\end{ex}

@@

\begin{ex}
:Anakin 
    :feelingForce 'true'^^xsd:boolean ;
    :attitute 'good'^^xsd:string ;
    :laserSwordColor 'blue'^^xsd:string ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
    :studentOf :Obi-Wan . 
\end{ex}

>>>>

A matching triple has any predicate except those excluded by the '!' operator.

\begin{ex}
<FeelingForce> {
    :feelingForce (true) ,
    :attitute xsd:string }
<JediMentor> {
    :feelingForce (true) ,
    :attitute ('good') ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
    :mentorOf @<JediStudent> ,
   !:studentOf @<JediMentor> }
<JediStudent> {
    :feelingForce (true) ,
    :attitute ('good') ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
   !:mentorOf @<JediStudent> ,
    :studentOf @<JediMentor> }
\end{ex}

@@

\begin{ex}
:Obi-Wan 
    :feelingForce true ;
    :attitute 'good' ;
    :laserSwordColor 'blue' ;
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
    :mentorOf :Anakin .
\end{ex}

@@

\begin{ex}
:Anakin 
    :feelingForce true ;
    :attitute 'good' ;
    :laserSwordColor 'blue' ;
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
    :studentOf :Obi-Wan .
\end{ex}
